---
title: "R Project 1 - Hello R"
author: "Aziz Surani"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

the dataset has 3 columns. A data frame with 1846 rows and 3 variables namely dataset, X: x-values, Y: y-values. 

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=6}
   star_data <- datasaurus_dozen %>%
   filter(dataset == "star")
   ggplot(data = star_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4



```{r plot-circle, fig.height=3, fig.width=6}
  circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
  ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5



```{r plot-comparision, fig.height=3, fig.width=6}
  ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```


```{r cor-comparision}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```









